%%COMMENT:2:12:Floating point puzzles (interesting values):
\begin{problem}{12}
Consider the following 16-bit floating point representation based on the
IEEE floating point format:
\begin{itemize}
\item There is a sign bit in the most significant bit.
\item The next seven bits are the exponent.  The exponent bias is 63.
\item The last eight bits are the significand.
\end{itemize}
The rules are like those in the IEEE standard (normalized,
denormalized, representation of 0, infinity, and NAN).

As described in Class 10, we consider the floating point format to
encode numbers in a form:
\begin{displaymath}
(-1)^s \times m \times 2^E
\end{displaymath}
where $m$ is the {\em mantissa} and $E$ is the exponent.



Fill in the table below
for the following numbers, with the following instructions for each column:
\begin{description}
\item[Hex:]
The 4 hexadecimal digits
describing the encoded form.  
\item[$m$:] The fractional value of the mantissa.  This should be a
number of the form $x$ or $x/y$, where $x$ is an integer, and $y$ is
an integral power of 2.  Examples include: 0, 67/64, and 1/256.
\item[$E$:]
The integer value of the exponent.
\item[Value:] The numeric value represented.  Use the notation
$x$ or $x \times 2^{z}$, where $x$ and $z$ are integers.
\end{description}

As an example, to represent the number $7/2$, we would have $s = 0$,
$m = 7/4$, and $E = 1$.  Our number would therefore have an exponent
field of {\tt 0x40} (decimal value $63+1 = 64$) and a significand
field {\tt 0xC0} (binary $11000000_2$), giving a hex representation
{\tt 40C0}.

You need not fill in entries marked ``---''.

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|l|c|c|c|c|}
\hline
Description & \makebox[.75in]{Hex} &
 \makebox[.75in]{$m$} & \makebox[.75in]{$E$} & \makebox[.75in]{Value} \\
\hline
$-0$ & & & & --- \\
\comment{
answer: & {\tt 8000} &  0 & -62 & -0 \\
}

\hline
Smallest value $> 1$ &&&&\\
\comment{
answer: & {\tt 3F01} & $257/256$ & 0 & $257/256$ \\
}


%% Omitted for time reasons
%%\hline
%%256 &&&& ---- \\
%%\comment{
%%answer: & {\tt 4700} & $1$ & 71 & --- \\
%%}


\hline
Largest Denormalized &&&& \\
\comment{
answer: & {\tt 00FF} & $255/256$ & -62 & $255 \times 2^{-70}$ \\
}
\hline
$-\infty$ & & --- & --- & --- \\
\comment{
answer: & {\tt FF00} & & & & \\
}
\hline
Number with hex representation {\tt 3AA0} &--- &&& \\
\comment{
answer: & & $13/8$ & $-5$ & $13/256$ \\
}
\hline
\end{tabular}
\end{center}

\end{problem}
