%%COMMENT:2:12:Floating point puzzles (interesting values):
\begin{problem}{12}
Consider the following 5-bit floating point representation based on the
IEEE floating point format.
There is a sign bit in the most significant bit.
The next three bits are the exponent, with an exponent bias is 3.
The last bit is the fraction.
The rules are like those in the IEEE standard (normalized,
denormalized, representation of 0, infinity, and NAN).

As described in Handout \#1, we consider the floating point format to
encode numbers in a form:
\begin{displaymath}
V \;\;=\;\; (-1)^s \times M \times 2^E
\end{displaymath}
where $M$ is the {\em significand} and $E$ is the {\em exponent}.

Fill in missing entries in the table below 
with the following instructions for each column:
\begin{description}
\item[Description:] Some unique property of this number, such as, ``The largest denormalized value.''
\item[Binary:]
The 5 bit representation.
\item[$M$:] The value of the Mantissa written in decimal format.
\item[$E$:]
The integer value of the exponent.
\item[Value:] 
The numeric value represented, written in decimal format.
\end{description}

You need not fill in entries marked ``---''.  For the arithmetic
expressions, recall that the rule with IEEE format is to round to the
number nearest the exact result.  Use ``round-to-even'' rounding.
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|l|c|c|c|c|}
\hline
\makebox[1.5in]{Description} & \makebox[.75in]{Binary} &
 \makebox[.75in]{$M$} & \makebox[.75in]{$E$} & \makebox[.75in]{Value} \\
\hline
Minus Zero & & & & $-0.0$ \\
\comment{ Answer & {\tt 10000} &  0 & $-2.0$ & \\
}
\hline
Positive Infinity & & --- & --- & $+\infty$ \\
\comment{Answer
& {\tt 01110} &  &  &  \\
}
\hline
& {\tt 01101} & & & \\
\comment{Answer
Largest Number & & $1.5$  & 3  & 12.0 \\
}
\hline
Smallest number $> 0$ & & & & \\
\comment{Answer
& {\tt 00001} & $0.5$  & $-2$  & $0.125$  \\
}
\hline
One & & & & $1.0$ \\
\comment{Answer
& {\tt 00110} & $1.0$ & $0$ & \\
}
\hline
$4.0-0.75$ &&&& \\
\comment{Answer
& {\tt 01001} & $1.5$ & $1$ & $3.0$ \\
}
\hline
$2.0+3.0$ &&&& \\
\comment{Answer
& {\tt 11010} & $1.0$ & $2$ & $4.0$ \\
}
\hline
\end{tabular}
\end{center}

\end{problem}
