%%COMMENT:6:7:High-level cache miss rate analysis:
\begin{problem}{7}

After watching the presidential election you decide to
start a business in developing software for electronic voting.
The software will run
on a machine with a 1024-byte direct-mapped data cache with 64 byte blocks.

You are implementing a prototype of your software that
assumes that there are 7 candidates. The C-structures you are using are:

\begin{verbatim}
struct vote {
    int candidates[7];
    int valid;
};

struct vote vote_array[16][16];
register int i, j, k;

\end{verbatim}

You have to decide between two alternative implementations of the routine
that initializes the array \verb|vote_array|. You
want to choose the one with the better cache performance.

You can assume:
\begin{itemize}
\item \verb|sizeof(int) = 4|
\item \verb|vote_array| begins at memory address 0
\item The cache is initially empty.
\item The only memory accesses are to the entries of the array \verb|vote_array|. 
Variables \verb|i|, \verb|j| and \verb|k| are stored in registers.
\end{itemize}

\end{problem}

A. What percentage of the writes in the following code will miss in the cache?

\begin{verbatim}

for (i=0; i<16; i++){
    for (j=0; j<16; j++) {
        vote_array[i][j].valid=0;
    }
}

for (i=0; i<16; i++){
    for (j=0; j<16; j++) {
        for (k=0; k<7; k++) {
            vote_array[i][j].candidates[k] = 0;
        }
    }
}

\end{verbatim}

% Answer: 2/16 = 12.5

\vspace{0.25in}

Total number of misses in the first loop: \verb|_______| \%

Total number of misses in the second loop: \verb|_______| \%

Overall miss rate for writes to \verb|vote_array|: \verb|_______| \%

\vspace{0.25in}

B. What percentage of the writes in the following code will miss in the cache?

\begin{verbatim}
for (i=0; i<16; i++){
    for (j=0; j<16; j++) {
        for (k=0; k<7; k++) {
            vote_array[i][j].candidates[k] = 0;
        }
        vote_array[i][j].valid=0;
    }
}

\end{verbatim}

% Answer: 1/16= 6.25

\vspace{0.25in}

Miss rate for writes to \verb|vote_array|: \verb|_______| \%

\vspace{0.25in}

