%%COMMENT:2:8:Floating point encoding:
\begin{problem}{8}
Consider the following 5-bit floating point representation based on the
IEEE floating point format:
\begin{itemize}
\item There is a sign bit in the most significant bit.
\item The next two bits are the exponent.  The exponent bias is 1.
\item The last two bits are the significand.
\end{itemize}
The rules are like those in the IEEE standard (normalized,
denormalized, representation of 0, $\infty$, and NAN).
As described in Class 10, the floating point format encodes
numbers in a form:
\begin{displaymath}
(-1)^s \times m \times 2^E
\end{displaymath}
where $m$ is the {\em mantissa} and $E$ is the exponent. 
The table below enumerates the entire non-negative range for this
5-bit floating point representation. Fill in the blank table entries
using the following directions:
\begin{description}
\item[$E$:] The integer value of the exponent.
\item[$m$:] The fractional value of the mantissa. 
{\bf Your answer must be expressed as a fraction of the form $x/4$.} 
\item[Value:] The numeric value represented.  {\bf Your answer
must be expressed as a fraction of the form $x/4$}.
\end{description}
You need not fill in entries marked ``---''.

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|l||c|c|c|}
\hline
{Bits} & \makebox[.75in]{$E$} &
\makebox[.75in]{$m$} & \makebox[.75in]{Value} \\
\hline
\hline
0 00 00 & --- &  ---  & 0 \\
%Answer: all zeros
\hline

0 00 01 &  &  &  \\
%Answer: 0 00 01 & $0$ & $1/4$ & $1/4$ \\
\hline

0 00 10 &  &  &  \\
%Answer: 0 00 10 & $0$ & $2/4$ & $2/4$ \\
\hline

0 00 11 &  &  &  \\
%Answer: 0 00 11 & $0$ & $3/4$ & $3/4$ \\
\hline

0 01 00 &  &  &  \\
%Answer: 0 01 00 & $0$ & $4/4$ & $4/4$ \\
\hline

0 01 01 &  &  &  \\
%Answer: 0 01 01 & $0$ & $5/4$ & $5/4$ \\
\hline

0 01 10 &  &  &  \\
%Answer: 0 01 10 & $0$ & $6/4$ & $6/4$ \\
\hline

0 01 11 &  &  &  \\
%Answer: 0 01 11 & $0$ & $7/4$ & $7/4$ \\
\hline

0 10 00 & $1$ & $4/4$ & $8/4$ \\
\hline

0 10 01 &  &  &  \\
%Answer: 0 10 01 & $1$ & $5/4$ & $10/4$ \\
\hline

0 10 10 & &  &  \\
%Answer: 0 10 10 & $1$ & $6/4$ & $12/4$ \\
\hline

0 10 11 &  &  &  \\
%Answer: 0 10 11 & $1$ & $7/4$ & $14/4$ \\
\hline

\end{tabular}
\end{center}

\end{problem}
